Convolutional equivalent layer \\ for magnetic data processing

### 2022-05-12 manuscript/submission_review_final.tex
manuscrito final para fist look

\section{Acknowledgments}
This study was financed by the brazilian agencies CAPES (in the form of a scholarship), FAPERJ
(grant n. E-26 202.729/2018) and CNPq (scholarship 300809/2022-0 and grants n. 309624/2021-5 and 315768/2020-7).

@@

\plot{Figure 2}{width=\textwidth}{
	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}, all of them with $N^{it} = 50$. The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
	\label{fig:flops}
}

@@

\tabl{RAM-usage}{This table shows the computer memory usage (in Megabytes) for storing the whole 
	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB
	matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 
	bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
	\label{tab:RAM-usage}}
{
	\begin{center}
		\begin{tabular}[]{|l|c|c|c|}
			\hline
			\textbf{$N$} & \textbf{$\mathbf{A}$} & \textbf{First columns of matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$} & \textbf{$\mathbf{L}$}\\
			\hline 
			$100$ & 0.0763 & 0.0183 & 0.00610\\
			\hline
			$400$ & 1.22 & 0.0744 & 0.0248\\
			\hline
			$2,500$ & 48 & 0.458 & 0.1528\\
			\hline
			$10,000$ & 763 & 1.831 & 0.6104\\
			\hline
			$40,000$ & 12,207 & 7.32 & 2.4416 \\
			\hline
			$250,000$ & 476,837 & 45.768 & 15.3 \\
			\hline
			$500,000$ & 1,907,349 & 91.56 & 30.518 \\
			\hline
			$1,000,000$ & 7,629,395 & 183.096 & 61.035 \\
			\hline
		\end{tabular}
	\end{center} 
}

>>>>

\section{Acknowledgments}
This study was financed by the brazilian agencies CAPES (in the form of a scholarship), FAPERJ
(grants n. E-26 202.729/2018 and 26/202.582/2019) and CNPq (scholarship n. 300809/2022-0 and grants n. 309624/2021-5 and 315768/2020-7). The authors thank the Geological Survey of Brazil (CPRM) for providing the field data, the editors and the reviewers that contibuted to this work.

@@

\plot{Figure 2}{width=\textwidth}{
	{Number of flops associated with classical method (equation \ref{eq:flops-classical-method}), the standard CGLS method (equation \ref{eq:flops-standard-cgls}) and our method (equation \ref{eq:flops-convolutional-method}), all of them with $N^{it} = 50$. The number of observation points $N$ varies from $5,000$ to $1,000,000$.}
	\label{fig:flops}
}

@@

\tabl{RAM-usage}{This table shows the computer memory usage (in Megabytes) for storing the whole 
	$N \times N$ matrix $\mathbf{A}$ (equation \ref{eq:A_expand}), the first columns of the BCCB
	matrices $\mathbf{C}_{\boldsymbol{\alpha\beta}}$ (equation \ref{eq:w_alpha_beta}) (both need 8 
	bytes per element) and the matrix $\mathbf{L}$ (equation \ref{eq:L}) (16 bytes per element).
	\label{tab:RAM-usage}}
